Reanalysis Step 7: Missingness Pattern Analysis

### 2025-09-01 reanalysis-7-missingness_patterns.qmd
fix ai idiiocy

# Additional packages for this analysis
library(readr)
library(knitr)
library(tableone)
library(ggplot2)
library(gridExtra)

@@

# Load the original data before exclusions
# This is the combined data file that includes all patients before any exclusions
original_data <- read_csv(reanalysis_data_file_path, show_col_types = FALSE)

@@

```{r variable-selection}
# Get variables used in outcome and propensity score models
# First, check what columns exist in the original data
cat("Columns in original data:\n")
cat(paste(names(original_data)[1:30], collapse = "\n"))
cat("\n...\n")

>>>>

# Additional packages for this analysis
library(knitr)
library(tableone)
library(ggplot2)
library(gridExtra)

@@

# Load the original data before exclusions
# Use the load_and_prepare_data function to get processed variables
original_data <- load_and_prepare_data(reanalysis_data_file_path)

@@

```{r variable-selection}
# Get variables used in outcome and propensity score models
# First, check what columns exist in the processed data
cat("Sample of columns in processed data:\n")
cat(paste(names(original_data)[1:min(30, length(names(original_data)))], collapse = "\n"))
cat("\n...\n")
cat("Total columns:", length(names(original_data)), "\n\n")
